\documentclass[12pt]{beamer}

\usetheme[sectionpage=none]{metropolis}
\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{Hard Disk Drive}}\xspace}


% make lists more compact:
\newlength{\wideitemsep}
\setlength{\wideitemsep}{.5\itemsep}
\addtolength{\wideitemsep}{-2pt}
\let\olditem\item
\renewcommand{\item}{\setlength{\itemsep}{\wideitemsep}\olditem}
\renewcommand{\arraystretch}{1.5}

\pretocmd{\tableofcontents}{\begin{minipage}{\textwidth}}{}{}
\apptocmd{\tableofcontents}{\end{minipage}}{}{}

% Presentation metadata
\title{Hard Disk Drives (HDD)}
\subtitle{A technical development journey}
\date{\today, Rapperswil}
\author{Cyrill Gsell \& Fabian Hauser}
\institute{Computer Science \\
	TecBEC Presentation FS 2016}

\begin{document}

\maketitle

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents
\end{frame}

\section{Introduction}
\section{What is a Hard Disk Drive?}
\begin{frame}[fragile]{What is a Hard Disk Drive?}
	\begin{itemize}
		\item Data storage
		\item How does it work?
			\begin{itemize}
				\item Rotating disk
				\item Magnetism tracks: ~75nm wide.
				\item Electronics
			\end{itemize}
	\end{itemize}
\end{frame}

\section{...but why can't we keep floppy disks?}
\begin{frame}[fragile]{...but why can't we keep floppy disks?}
	HDDs are better considering:
	\begin{itemize}
		\item Capacity
		\item Durability
		\item Price
		\item Efficiency / Speed
	\end{itemize}		
\end{frame}

\section{Evolution}
\begin{frame}[fragile]{Evolution: First attempts}
	TODO!
\end{frame}

\begin{frame}[fragile]{Evolution: Development}
	TODO!
\end{frame}


\begin{frame}[fragile]{Evolution: State of the art}
	TODO!
\end{frame}

\section{A glance into the future}
\begin{frame}[fragile]{A glance into the future}
	\begin{itemize}
		\item	SSHD: SSD and HDD combined \\
				$\rightarrow$ good price \& capacity
		\item	Physical storage density limit: ~75nm tracks. \\
			Work arounds:
			\begin{itemize}
				\item	Helium filling
				\item	SHT
				\item	TDMR
			\end{itemize}
		\item	In many areas superseded with SSDs
	\end{itemize}
\end{frame}
\note[itemize]{
	\item SMR (Shingle Magnetic Recording) Overlying the tracks
	\item TDMR (Two-Dimensional Magnetic Recording)
}

\section{Questions}
\begin{frame}[standout]
	Questions? \\
	Thank you for your interest!
\end{frame}

\begin{frame}[fragile]{Ressources}
	\begin{itemize}
		\item \url{http://www.ewh.ieee.org/r6/scv/mag/MtgSum/Meeting2010_10_Presentation.pdf}
	\end{itemize}
\end{frame}


\end{document}
